%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A modern, clean, and professional resume template in LaTeX
%
% © 2024 by AI
%
% This template is free to use and distribute.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt, a4paper]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{needspace} 

% --- PAGE LAYOUT ---
\geometry{
    a4paper,
    left=0.75in,
    right=0.75in,
    top=0.75in,
    bottom=0.75in
}

% --- HYPERLINK SETUP ---
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    pdftitle={Debarun Lahiri - Resume},
    pdfauthor={Debarun Lahiri},
}

% --- SECTION FORMATTING (CORRECTED) ---
% This now correctly targets the unnumbered \section* commands
\titleformat{name=\section, numberless}{\Large\bfseries\scshape\raggedright}{}{0em}{\Needspace{5\baselineskip}}[\titlerule]
\titlespacing*{name=\section, numberless}{0pt}{1.5ex}{1ex}

% --- CUSTOM COMMANDS ---
% For a compact bullet point item
\newcommand{\resumeItem}[1]{
    \item\small{#1}
}

% --- DOCUMENT START ---
\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \scshape Debarun Lahiri}
    \vspace{1ex}
    
    \href{mailto:debarunlahiri2016@gmail.com}{debarunlahiri2016@gmail.com} \quad\textbar\quad
    \href{https://debarunlahiri-web.vercel.app/}{debarunlahiri.lambrk.com} \quad\textbar\quad Noida, UP, India \quad\textbar\quad
    +91-9205225428
\end{center}

% --- KEY SKILLS ---
\section*{Key Skills}
\begin{itemize}[leftmargin=*, label={}, itemsep=0.25ex]
    \item \textbf{Programming Languages:} Java, Kotlin
    \item \textbf{Mobile Development:} Android (Java and Kotlin), React Native, Ionic
    \item \textbf{Web Development:} Angular, React, NextJs, Javascript, HTML, CSS
    \item \textbf{Backend Development:} Spring Boot, RESTful APIs, Microservices, Kafka
    \item \textbf{Cloud, Tools \& AI:} Firebase, ML Kit, Google Cloud, Jetpack Compose, AWS
    \item \textbf{Databases:} Oracle SQL, PostgreSQL, MySQL, RoomDB
    \item \textbf{Soft Skills:} Leadership, Agile Methodologies, Problem Solving
\end{itemize}

% --- EXPERIENCE ---
\section*{Experience}
\begin{itemize}[leftmargin=0pt, itemsep=1ex, topsep=0.5ex, partopsep=0pt]
    \item
    \textbf{Samsung Display Noida} \hfill \textbf{Noida, UP, India} \\
    \textit{Senior Assistant Engineer} \hfill \textit{Dec 2022 – Present}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.5ex, topsep=0.5ex]
        \resumeItem{OCR System Development: As Tech Lead, led the design and implementation of an Optical Character Recognition (OCR) system using ML Kit. The system significantly improved data extraction efficiency by 20\%, enabling faster decision-making and reducing manual effort in data processing.}
        \resumeItem{Web Portal Design and Implementation: Designed and developed a user-centric web portal that streamlined business operations and enhanced the user experience by optimizing the layout, navigation, and overall usability. Resulted in a 15\% increase in platform functionality and a smoother interface.}
        \resumeItem{NLP ChatBot Development: Lead the development of a natural language processing-powered chatbot, which reduced customer response time by 40\%. This tool provided real-time assistance, improving customer satisfaction and automating routine inquiries.}
        \resumeItem{Cross-functional Collaboration for Manufacturing Optimization: Collaborated with cross-functional teams, including engineers and product managers, to deliver solutions that improved manufacturing efficiency by 15\%, leading to a reduction in production downtime and a more optimized workflow.}
    \end{itemize}
    
    \item
    \textbf{TraqIQ} \hfill \textbf{Noida, UP, India} \\
    \textit{Software Engineer} \hfill \textit{Nov 2021 – Dec 2022}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.5ex, topsep=0.5ex]
        \resumeItem{Paytm Payment Gateway Integration: Integrated Paytm Payment Gateway into Spring Boot applications, ensuring secure and seamless transactions for thousands of users. This integration improved payment processing efficiency and significantly reduced transaction failures.}
        \resumeItem{UI Performance Optimization: Developed dynamic, responsive user interfaces, reducing page load times by 30\%. Leveraged frontend optimization techniques, including lazy loading and asynchronous data fetching, to enhance the overall performance and user experience.}
        \resumeItem{Hybrid Mobile App Development: Developed a high-performance, cross-platform hybrid mobile app using React Native Framework, ensuring responsive design and functionality across both iOS and Android platforms. The app streamlined internal processes and enhanced user engagement.}
    \end{itemize}
    
    \item
    \textbf{Bnext IT Solutions} \hfill \textbf{Noida, UP, India} \\
    \textit{Android Developer} \hfill \textit{May 2021 – Nov 2021}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.5ex, topsep=0.5ex]
        \resumeItem{App Performance Optimization: Enhanced mobile app performance, leading to a 25\% increase in user retention by identifying and fixing key bottlenecks and bugs through rigorous testing and debugging.}
        \resumeItem{OneSignal Integration for Notifications: Integrated OneSignal for push notifications and Google Play Payment Gateway, ensuring seamless transaction processing and real-time communication with users.}
    \end{itemize}
    
    \item
    \textbf{Grepix Infotech Private Limited} \hfill \textbf{Noida, UP, India} \\
    \textit{Android Developer} \hfill \textit{Jan 2020 – Feb 2021}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.5ex, topsep=0.5ex]
        \resumeItem{Responsive UI Development: Designed and developed responsive mobile and tablet applications, improving accessibility for users across various devices. The design improvements increased user engagement and app usage.}
        \resumeItem{Google Maps API Integration: Integrated Google Maps APIs into mobile apps to enhance functionality with real-time location-based services, providing users with enhanced navigation and location tracking features.}
    \end{itemize}
\end{itemize}
    
% The \newpage command forces this content onto the next page.
\newpage
    
% --- EXPERIENCE (CONTINUED) ---
\begin{itemize}[leftmargin=0pt, itemsep=1ex, topsep=0.5ex, partopsep=0pt]
    \item
    \textbf{Rounderlabs Private Limited} \hfill \textbf{Noida, UP, India} \\
    \textit{Android Developer} \hfill \textit{Jun 2019 – Dec 2019}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.5ex, topsep=0.5ex]
        \resumeItem{Authentication Services: Implemented multiple authentication services including mobile, Facebook, Google and email login, greatly improving app security and providing users with multiple secure login options.}
        \resumeItem{Video Streaming Optimization: Worked on optimizing a video streaming application, improving its performance by reducing buffering times and ensuring smoother playback even with lower network speeds.}
    \end{itemize}
\end{itemize}

% --- PROJECTS ---
\section*{Projects}
\begin{itemize}[leftmargin=1.5em, itemsep=0.75ex, topsep=0.5ex, label=\textbullet]
    \resumeItem{\textbf{Vani AI- Speech-To-Text: } Vani AI is an offline speech-to-text mobile app where users speak into the device. Python handles audio processing with automatic language detection using the Whisper model, then generates text and translations to English, Hindi, and Korean via ArgosTranslate. Node.js serves as a proxy for API calls, while a separate Python API focuses on audio and translation. The Node.js website allows viewing, playing recordings, and accessing translations—all processed locally without internet. (\textit{Tech Stack: Kotlin, Android, Python, NodeJs, Javascript})}
    \resumeItem{\textbf{OTR - Operator Training Records:} Led the design, development, and deployment of an Android application for Operator Training Records (OTR), aimed at providing operators with convenient access to their training records and compliance status. Enhanced usability based on user feedback, leading to increased user engagement. (\textit{Tech Stack: Java, Kotlin, Spring Boot, Angular})}
    \resumeItem{\textbf{Chat Bot:} Designed conversational flows and integrated NLP models to enable the ChatBot to understand and respond to user inquiries effectively. Conducted A / B testing and collected user feedback to iterate on ChatBot features, resulting in a 40\% reduction in customer response times and improved customer satisfaction scores. (\textit{Tech Stack: Java, Android, Kotlin, NLP, Spring Boot, Oracle SQL})}
    \resumeItem{\textbf{Motion Tracking:} Developed an application to track the motion of objects/equipment on the production line and generate related graphs for analysis purposes. The results can be tracked through a mobile app or a Monitoring Portal for real-time insights. (\textit{Tech Stack: Java, Android, Firebase, OpenCV, Spring Boot})}
    \resumeItem{\textbf{e-VIS (Violation Information System):} Developed an Android application for the Manufacturing Department to manage violations committed by operators at the production line. Successfully implemented a record of violations within the system, allowing efficient tracking, reporting, and management of violations in multiple locations or departments. (\textit{Tech Stack:  Kotlin, Java, Spring MVC, Node.js, Oracle SQL})}
    \resumeItem{\textbf{LMS - Learning Management System:} Collaborated in a team of 7 developers to design, develop, and deploy a Learning Management System (LMS) for managing skills and training for Persons in Charge (PICs) and departments. Using technologies like Spring MVC to create interactive interfaces for course enrollment, content delivery, assessments, and progress tracking. (\textit{Tech Stack: Spring Boot, Java, Oracle SQL, Angular, RxJS, Microservices, AWS, Kafka})}
    \resumeItem{\textbf{HireMe Driver \& Rider:} Developed a cab booking app where users can book cabs and reach their destinations. Provided a platform for both riders and drivers to manage bookings. Worked on Backend for RestAPI. (\textit{Tech Stack: Java, Kotlin, Android, Firebase, Google Maps API, WebSockets})}
    \resumeItem{\textbf{TraqPayments:} Built a payment and collection management system, with multi-channel communication tools for customers and optimized backend operations. Provided an Android app for customer access.
   Worked on Backend for RestAPI and web portal for managing payments.(\textit{Tech Stack: Java, Android, Kotlin, Angular, Spring Boot, MySQL})}
    \resumeItem{\textbf{PictureTime \& Filamchi:} Developed and maintained the PictureTime and Filamchi apps. Focused on mobile development and implemented back-end optimizations to improve response times and system reliability. (\textit{Tech Stack: React Native, Java, Firebase, Microservices, Spring Boot, iOS})}
    \resumeItem{\textbf{Masala Dish (Customer, Driver \& Restaurant Manager):} Spearheaded the development of the Masala Dish Android application, providing a platform for customers, drivers, and restaurant managers in the food delivery ecosystem. Improved app performance with faster load times and smoother navigation. Worked on Backend for RestAPI and web portal. (\textit{Tech Stack: Kotlin, Microservices, Spring Boot})}
    \resumeItem{\textbf{OnDemand Services:} Led the development of an On-Demand Services Android application, offering services to customers. Integrated real-time communication between customers and service providers to improve service delivery. Worked on Backend for RestAPI and web portal. (\textit{Tech Stack: Java, Kotlin, Firebase, WebSockets, Angular, Spring Boot})}
    
\end{itemize}

% --- EDUCATION ---
\section*{Education}
\begin{itemize}[leftmargin=0pt, itemsep=1ex, topsep=0.5ex, partopsep=0pt]
    \item
    \textbf{Institute of Management and Studies, Ghaziabad} \hfill \textbf{Ghaziabad, India} \\
    \textit{Bachelor of Computer Applications (BCA)} \hfill \textit{2016 – 2019}
    
    \item
    \textbf{D.D.M. Public School} \hfill \textbf{Ghaziabad, India} \\
    \textit{Class 12th (C.B.S.E. Board)} \hfill \textit{2015}
    
    \item
    \textbf{D.D.M. Public School} \hfill \textbf{Ghaziabad, India} \\
    \textit{Class 10th (C.B.S.E. Board)} \hfill \textit{2013}
\end{itemize}

\end{document}

